A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-11 paper.tex
comment and edits to abstract

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, notably coercions in normal forms and threesomes. But they are
presented in different dynamic semantics, which make it difficult to compare
the key differences between the cast representations. We present a abstrat
data type, namely Cast ADT, that captures interface functions a cast representations
typically includes, and an abstract machine parameterized over Cast ADTs.
The Cast ADT brings another benefit: space-efficient cast representations 
shall be proved not changing the 
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving properties
of a specific Cast ADT, which is simpler than going through a bisimulation proof 
between a space-efficient dynamic semantics and the definitional dynamic semantics.
We have successfully applied our new approach of proving the correctness of cast 
representations to several known cast representations
(\cite{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968})
and believe this framework
is also applicable to other cast representations (\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).
We also present a new cast representation, hypercoercions, that is more friendly
to mechanized meta-theory and consumes less memory than coercions
in normal forms.

\todo[inline]{KC: I feel ``going through a bisimulation proof'' is too specific.
There should be other ways to prove equivalence of two dynamic semantics.
How does Jeremy think?}

>>>>

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing combines dynamic typing and static typing in one
language to provide the advantages of both typing
disciplines. Implementing gradual typing with reasonable overhead,
however, is not trivial. Casts accumulate on higher-order values and
continuations, changing the overall space complexity. Several
space-efficient cast representations have been proposed, notably
coercions in normal forms and threesomes. But they are presented in
different dynamic semantics, which make it difficult to compare the
key differences between the cast representations. We present a
abstract data type, namely Cast ADT, that captures interface functions
a cast representations typically includes, and an abstract machine
parameterized over Cast ADTs.  The Cast ADT brings another benefit:
space-efficient cast representations shall be proved not changing the
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving
properties of a specific Cast ADT, which is simpler than proofs
regarding the entire dynamic semantics.
\todo[inline]{JS: The stuff above about ``make it difficult to compare''
  is a weak argument. I would recommend deleting that argument and
  instead focus on the benefits regarding the proofs of correctness.}

We have successfully applied our new approach to the proofs of
correctness for two space-efficient cast representations from the
literature
(\cite{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968})
and believe this framework is also applicable to other cast
representations
(\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).  We
also present a new cast representation, hypercoercions, that is more
friendly to mechanized meta-theory and consumes less memory than
coercions in normal forms. We prove correctness for two variants of
hypercoercions.

\todo[inline]{KC: I feel ``going through a bisimulation proof'' is too specific.
There should be other ways to prove equivalence of two dynamic semantics.
How does Jeremy think?}
\todo[inline]{JS: yes}
